\plaintitle

### 2016-05-27 cscw/papers/2017/labor/trackingWork.tex

\section{Introduction}
The past decade has seen
microtasks, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has made connections between this emergent form of work
and the historically situated ``piecework'',
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work
\cite{turkopticon,dynamo,uberAlgorithm}.
But the connections between
historical piecework and
contemporary crowd work
haven't been deeply made as yet.
% um, note to self: say more.

While much of this work appears to gesture toward
the parallels between contemporary on--demand work and piecework,
it's proven difficult to bring the totality of these observations into focus using one theoretical lens.
This paper will attempt to do so by arguing that
the topics social computing researchers have investigated are
not just parallel to historical piecework and
the process of factorization that took place in the early \nth{20} century;
indeed, these phenomena precipitate and reinforce each other.

In the reflection on the literature published in the last 5 years since
\citeauthor{crowdworkFuture}'s 
\citetitle{crowdworkFuture},
we notice a broader trend describing the change in work that's being done
\cite{crowdworkFuture}.
Following the improvements in
breaking down tasks,
delegating work, and
managing workers more broadly,
Crowd--powered has continued to parallel historical piecework's trajectory
by outgrowing ad--hoc worker groups and coalescing into more formal working groups;
we might call this the beginning of factorization.
% "Factorization" is not the right word but I honestly have no idea what the right term is.
% The process of formalizing work into factories? Should I tweet/post/ask about this somewhere?

% Crowd work,
% they argued in \citeyear{crowdworkFuture},
% represents a threat to the future of work inasmuch as it marginalized
% and perhaps even harmed
% workers;
% their driving question, then, was
% whether the future of
% (crowd, but arguably all discretized)
% work might be one in which they wish their children to participate someday;
% it seems strikingly like one that might have been asked
% as patches of denim were first being delivered to the homes of early pieceworkers.
% agreed; i'm commenting it out for now to see how I feel without making this argument at all. If I really feel like it's missing, I should find evidence that contemporaries discussed it...

Making sense of this 
by looking at the movements toward
distributing work,
routinizing and breaking down tasks,
and externally managing workers
as linked to one another, 
we give ourselves a framing of contemporary piecework that explains,
and arguably predicts,
what we have seen thus far
--- and perhaps what we should expect to see going forward.

This paper will attempt to demonstrate that the familiarity is more than passing;
that the phenomena researchers have observed in on--demand digitally mediated labor markets
were inevitable milestones in the birth and life of piecework.
We will set out to show that this perspective of crowd work as an embodiment of piecework
predicts the myriad outcomes of contemporary crowd work, including
our developments of work--flows further abstracting work,
the troubling effects of those developments on factors such as pay and work quality, and
many if not all of the frustrations researchers have discovered among workers
in the study of crowd and gig work.

``But'',
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor there is nothing new under the sun''
\cite{scholz2012digital}.
For one, information work
(e.g. AMT \& Upwork)
and digitally managed work in general make it substantially easier
to keep workers geographically dispersed
compared to the factory workers that followed home--based piecework.
This aspect of work renders workers virtually invisible to the task solicitors
--- or ``requesters'' ---
despite being significantly more connected than historical pieceworkers were % this is a weak point...
\cite{turkopticon}.
Secondly, while
factory foremen and other middle--men
traditionally mediated the relationships between workers and managers,
today the visible agents are \textit{systems};
rather than employing individuals who ``personified the functions of management''
and can thus negotiate workers' needs,
socio--technical systems mediate these interactions % often with unrewarding outcomes
\cite{wray1949marginal}.
% \cite{storiesIraniSilberman}.
Finally, this characteristic of modern piecework makes
worker coordination for collective advocacy and action significantly more difficult,
necessitating special consideration to maintain the inertia of collective will
while focusing that energy productively
\cite{dynamo}.
% \ali{I really don't like this paragraph\dots}
% here are undoubtedly more examples of differences.
% How do I not stake a claim that this is comprehensive?
% Or should I really flesh this out and make it (comprehensive)?

@@

\citeauthor{crowdworkFuture}
write of the future of crowd work in an effort to investigate
whether crowd work will be a worthwhile form of work or another instantiation of ``piecework'',
a term historically used to describe work done in the home,
in manageable tasks,
often involving clear instructions
and payment only for work completed, not work done
(the differentiation, here, being that
one would be paid for the \textit{output} of the work,
not the \textit{duration})
\cite{crowdworkFuture}.
% \msb{is that true? by that definition, design is piecework too, right, because I get paid for the job, not for hours worked. But design doesn't seem like piecework.}.
% This work was largely in textiles and was predominantly done by women,
% which by itself is a topic worthy of unpacking
% \msb{instead of gesticulating, can we indicate what the punchline of unpacking it was?}
% \ali{let's just leave this in the graveyard for now; i feel like someone who knows what they're talking about with regard to feminist and gender studies
% (e.g. the Bardzells, Irani) would really do justice here, but i'd be getting in over my head}
% \cite{scott1975women}.
Given the scope,
we can frame piecework and gig work as sharing these important similarities:
\begin{inlinelist}
\item this form of work began in the home
\item the worker is paid for each discrete piece of work done, regardless of time or effort; and
\item the worker's status
(not only socially, but also economically)
is ambiguous, or at least the subject of some controversy.
\end{inlinelist}.

@@

This paper attempts to make sense of the broader research on this new form of labor,
or ``gig work'', by evaluating this work through a more familiar lens: piecework.
More concretely, by looking at task--based or ``gig'' work as
an instantiation and continuation of piecework,
and by looking for patterns of behavior that the corresponding literature predicts
on this basis, we can do the following:
\begin{inlinelist}
  \item we can make sense of the phenomena so far as part of a much larger series of interrelated events;
  \item we can bring into focus the ongoing work among workers, system--designers, and researchers in this space; and finally,
  \item we can offer predictions of what social computing researchers, and workers themselves, should expect to see on the horizon of on--demand work.
\end{inlinelist}

@@

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the \textbf{processes} involved in making work into tasks, or discretization;
\item the outcomes (and indeed the \textbf{fallout}) of that discretization,
both on the work itself as well as the workers;
and finally
\item the \textbf{relationships} between workers and requesters of the work
--- both \textit{cooperative} and \textit{adversarial} cases.
\end{enumerate}

@@

\subsubsection{Decomposition}\label{sec:decomposition}
Piecework may be thought of as vertically slicing work such that 
each person is responsible for the whole task
--- making a whole garment, in this case.
Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable.
Textile work being a salient example,
it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work.
% some seamstresses might be better than others at the same task,
% making this framing of the work initially problematic.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,
manageable routines that could be taught relatively easily,
and whose work output could be evaluated in abstraction from the rest of the work.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,
but a single very narrowly defined action that needed to be done on every car.

This approach paralleled what would be known as ``Taylorism'',
and its influences can be seen today in crowd work and micro--tasks.
\textit{talk about breaking tasks down both in general (Cheng) and even for the self (Teevan);
horizontal cuts instead of vertical}
\cite{cheng2015break,writingMicroTasks}.
By decomposing and recomposing tasks,
and in particular by assigning similarly natured work to the same workers,
% and especially as the nature of the work could be aligned with other, similar tasks,
workers could become ``experts'' in a small aspect of the work that they did,
speeding their work dramatically
\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage
[\textit{citation needed}].

Scholarship describing and exploring
the decomposition of tasks is perhaps the most established of the above areas among HCI researchers;
\citeauthor{bernsteinSoylent} made early contributions to this area with \textit{Soylent}
(by coining and employing the ``find--fix--verify'' approach)
\cite{bernsteinSoylent}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work might be readily interrupted
\cite{cheng2015break}.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work
by exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While this work doesn't strictly fall under ``crowdsourcing'',
the major contributions here
seem uncontroversially to be inspired by the design of crowd work.

@@

% In both the historical and contemporary cases,
% distributed, speculative work
% has promised
% to diffuse the costs of capital--intensive resources
% (whether they were sewing machines or laboratory equipment).

@@

\subsubsection{Flexibility}\label{sec:flexibility}
Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance.
This work both points to and embodies a broader sentiment in
both the study and practice
of crowd work that microtasks should be designed flexibly,
fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
While \citeauthor{cheng2015break} identified costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization),
\citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together.

@@

\citeauthor{embracingErrorKrishna} offer orders--of--magnitude improvements
in various binary classification tasks
% --- a typical application crowd work ---
on the principle that myriad diverse workers complete these tasks
in order to accurately inform the model.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of this phenomenon:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

@@

\subsubsection{Low Pay}\label{sec:lowPay}
\citeauthor{laborEconomicsOfCrowdsourcingHorton}
identified problems with crowd work wages relatively early on,
attempting to address this imbalance from a behavioral economic perspective ---
that is, identifying and presenting a model that describes a worker's
``\textit{reservation wage}''
\cite{laborEconomicsOfCrowdsourcingHorton}.
This work has largely informed much of the research into and practice of estimating crowd work compensation
\cite{incentivesShaw,paolacci2010running}.
More cynically,
we would describe this work as identifying optimal levels to activate race conditions among piece workers.

@@

\subsubsection{Variable quality work}\label{sec:varQualWork}
Meanwhile,
researchers have struggled with what we might call ``variable quality work''
along two dimensions:
First, to use the characterization of one of these contributions,
``understanding malicious behavior''
\cite{MaliciousCrowdworkersGadiraju}.
While some work has cast workers as ``malicious'' agents,
the evidence thus far suggests that
workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
(a topic of discussion to which we'll return later)
\cite{uberAlgorithm}.
The second dimension of research in this space generally attempts
to eke out the highest quality work possible from workers
given the apparent difficulty in predicting work outcomes

@@

Suffice it to say, then, that poor pay and poor work are linked,
and that we should not be surprised to find this relationship play out online as strongly as it does offline.
Indeed,

>>>>

\section{Introduction}
% \msb{I think a contribution of this paper can be, and should be, unifiying crowd work, sharing economy, and gig economy all under one theoretical banner: piecework. Come out and say that super visibly somewhere in this intro as a major contribution.}

The past decade has seen
paid microtasking, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has made connections between this emergent form of work
and the historically situated ``piecework'',
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work,
but situating the causes of these frustrations either in the larger body of scholarship on crowd work,
or crowd work itself,
has proven difficult;
% as a result,
the connection between crowd work and a historical parallel contextualizing its ongoing developments 
hasn't been deeply made yet
\cite{turkopticon,dynamo,uberAlgorithm}.
% \msb{A weak differentiating sentence: }
% But the connections between
% historical piecework and
% contemporary crowd work
% haven't been deeply made as yet.
% um, note to self: say more.
% \msb{This paragraph doesn't set up the tension and release effectively. I suggest focusing this paragraph on a brief summary of the things that people have pointed out (low pay, Taylorism, difficult collective action). Basically paint them as a bunch of disconnected observations --- which is what they have been. Then at the start of the next paragraph, come out with a clear and visible thesis: say that all of these things fall under the banner of piecework. (and now you can finally mention that while piecework has been brought up, nobody has made the historical connections yet) Then you can move on to the next paragraph below, which is about how it's basically a necessary outcome.}

While much of this work appears to gesture toward
the parallels between contemporary on--demand work and piecework,
it's proven difficult to bring the totality of these observations into focus using one theoretical lens.
This paper will attempt to do so by arguing that
the topics social computing researchers have investigated are
not just parallel to historical piecework and
the process of factorization that took place in the early \nth{20} century;
indeed, these phenomena \textit{precipitate and reinforce each other}.

In the reflection on the literature published in the last 5 years since
\citeauthor{crowdworkFuture}'s 
\citetitle{crowdworkFuture},
we notice a broader trend describing the change in work that's being done
\cite{crowdworkFuture}.
Following the improvements in
breaking down tasks,
delegating work, and
managing workers more broadly,
crowd--powered work has continued to parallel historical piecework's trajectory
by outgrowing ad--hoc worker groups and coalescing into more formal working groups,
for example through the use of a ``white list'' of familiar workers.
We might call this the regularization of factory work.

Making sense of the broader field of crowd work
by looking at the movements toward
distributing work,
routinizing and breaking down tasks,
and externally managing workers
as linked to one another, 
we give ourselves a framing of contemporary piecework that explains,
and arguably predicts,
what we have seen thus far
--- and perhaps what we should expect to see going forward.

This paper will attempt to demonstrate that the familiarity
that we incidentally observe between what we generally call crowd work \& gig work
and the historical practice of piecework and subsequent factory work
is more than passing;
that the phenomena researchers have observed in on--demand digitally mediated labor markets
were inevitable milestones in the birth and life of piecework.
We will set out to show that this perspective of crowd work as an embodiment of piecework
predicts the myriad outcomes of contemporary crowd work, including
our developments of work--flows further abstracting work,
the troubling effects of those developments on factors such as pay and work quality, and
many if not all of the frustrations researchers have discovered among workers
in the study of crowd and gig work.

``But'',
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor there is nothing new under the sun''
\cite{scholz2012digital}.
For one, information work
(e.g. Amazon Mechanical Turk (AMT) \& Upwork)
and digitally managed work in general make it substantially easier
to keep workers geographically dispersed
compared to the factory workers that followed home--based piecework.
This aspect of work renders workers virtually invisible to the task solicitors
--- or ``requesters'' ---
despite being significantly more connected than historical pieceworkers were % this is a weak point...
\cite{turkopticon}.
Secondly, while
factory foremen and other middle--men
traditionally mediated the relationships between workers and managers,
today the visible agents are \textit{systems};
rather than employing individuals who ``personified the functions of management''
and can thus negotiate workers' needs,
socio--technical systems mediate these interactions % often with unrewarding outcomes
\cite{wray1949marginal}.
% \cite{storiesIraniSilberman}.
Finally, this characteristic of modern piecework makes
worker coordination for collective advocacy and action significantly more difficult,
necessitating special consideration to maintain the inertia of collective will
while focusing that energy productively
\cite{dynamo}.
% \ali{I really don't like this paragraph\dots}
% here are undoubtedly more examples of differences.
% How do I not stake a claim that this is comprehensive?
% Or should I really flesh this out and make it (comprehensive)?

@@

\citeauthor{crowdworkFuture}
write of the future of crowd work in an effort to investigate
whether crowd work will be a worthwhile form of work or another instantiation of ``piecework''
\cite{crowdworkFuture}.
``Piecework'' here makes use of
a term historically used to describe work done in the home,
in manageable tasks,
often involving clear instructions
and payment only for work completed, not work done
(the differentiation, here, being that
one would be paid for the \textit{output} of the work,
not the \textit{duration}).
% \msb{split up that sentence. One is the def'n of piecework, the other is the comparison you're drawing}
Given the scope,
we can frame piecework and on--demand labor
% \msb{
% \sout{wait, are you using gig work as the umbrella term? I think you need a category term that covers all of them}
% \ali{let's use ``on--demand labor'', since
% that seems general enough without accidentally including historical piecework}}
as sharing these important similarities:
\begin{inlinelist}
\item this form of work began in the home
\item the worker is paid for each discrete piece of work done, regardless of time or effort; and
\item the worker's status
(not only socially, but also economically)
is ambiguous, or at least the subject of some controversy.
\end{inlinelist}.

@@

This paper attempts to make sense of the broader research on this new form of work,
\textit{on--demand labor}, by evaluating this work through a more familiar lens: piecework.
More concretely, by looking at task--based or ``gig'' work as
an instantiation and continuation of piecework,
and by looking for patterns of behavior that the corresponding literature predicts
on this basis, we can do the following:
\begin{inlinelist}
  \item we can make sense of the phenomena so far as part of a much larger series of interrelated events;
  \item we can bring into focus the ongoing work among workers, system--designers, and researchers in this space; and finally,
  \item we can offer predictions of what social computing researchers, and workers themselves, should expect to see on the horizon of on--demand work.
\end{inlinelist}

@@

\section{Case Studies}
The existing body of research has shed light on on--demand labor from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the \textbf{processes} involved in making work into tasks, or discretization;
\item the outcomes (and indeed the \textbf{fallout}) of that discretization,
both on the work itself as well as the workers;
and finally
\item the \textbf{relationships} between workers and requesters of the work
--- both \textit{cooperative} and \textit{adversarial} cases.
\end{enumerate}

@@

\subsubsection{Decomposition}\label{sec:decomposition}
Piecework may be thought of as vertically slicing work such that 
each person is responsible for the whole task
--- making a whole garment, in this case.
Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example,
it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,
manageable routines that could be taught relatively easily,
and whose work output could be evaluated in abstraction from the rest of the work
\cite{restructuringPieceworkBaker}.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,
but a single very narrowly defined action that needed to be done on every car
\cite{towardsGlobalFordism}.
By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes,
``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''
\cite{schoenberger1988fordism}.

This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos),
can be seen today in crowd work and on--demand labor through the application of micro--tasks.
\citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces,
facilitating evaluation and parallelization
\cite{writingMicroTasks}.
By decomposing and recomposing tasks,
and in particular by assigning similarly natured work to the same workers,
workers could become ``experts'' in a small aspect of the work that they did,
speeding their work dramatically
\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage
\cite{rogstadius2011assessment}.

Scholarship describing and exploring
the decomposition of tasks is perhaps the most established of the above areas among HCI researchers;
\citeauthor{crowdForgeKittur} specifically drive at this goal by addressing the possibility of
``crowdsourcing complex work''
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work might be readily interrupted
\cite{cheng2015break}.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work
by exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While this work doesn't strictly fall under ``crowdsourcing'',
the major contributions here
seem uncontroversially to be inspired by the design of crowd work.

@@

@@

\subsubsection{Flexibility}\label{sec:flexibility}
% \msb{nothing in this subsubsection connects to the piecework literature. bring it back!}

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance.
This work both points to and embodies a broader sentiment in
both the study and practice
of crowd work that microtasks should be designed resiliently against the variability of workers,
% \msb{not sure what flexibly means here, and the rest of the sentence isn't helping me unpack it. flexibility for requester? worker? flexible algorthms?},
fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance,
or a good worker's sudden departure,
would not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} identified costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization),
\citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together.

@@

\citeauthor{embracingErrorKrishna} offer orders--of--magnitude improvements
in various binary classification tasks
on the principle that diverse workers complete these tasks
in order to accurately inform the model on the variety of delays in response times.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of this phenomenon:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

Flexibility has been explored through the lens of Fordism, perhaps best illustrated by
\citeauthor{tolliday1986between}'s treatment describing
turnover rates rising above 300\% in the decade leading to the introduction of the assembly line in 1913.
Specifically, the utilization of ``\dots~`semi--special' machine tools which could be adapted
[and]~\dots~added flexibility through seasonal layoffs for production workers and the use of
piece rates~\dots~rather than a day wage system''
\cite{tolliday1986between}.

% \msb{I still dont' have a clear conceptual picture of what flexibility is, and what about it sets this section apart. Ranjay's stuff is about speed...? I'm confused.}

@@

\subsubsection{Low Pay}\label{sec:lowPay}
% \msb{nothing in this subsubsection connects to the piecework literature. bring it back!}

\citeauthor{laborEconomicsOfCrowdsourcingHorton}
identified problems with crowd work wages relatively early on,
attempting to address this imbalance from a behavioral economic perspective ---
that is, identifying and presenting a model that describes a worker's
``\textit{reservation wage}''
\cite{laborEconomicsOfCrowdsourcingHorton}.
This work has largely informed much of the research into and practice of estimating crowd work compensation
\cite{incentivesShaw,paolacci2010running}.
More cynically,
we would describe this work as identifying optimal levels to activate race conditions \msb{???} among piece workers.

@@

Turmoil over low --- and declining --- pay was among the chief grievances among then nascent
British labor unions in the early \nth{20} century
\cite{turner1952trade}.
This, \citeauthor{ebbinghaus1999institutions} argued,
fueled the rocketing union membership rates through the mid--\nth{20} century until 1980
(to which we'll return later when we discuss \citeauthor{levi2009union}'s reexamination of labor advocacy organizations)
\cite{ebbinghaus1999institutions}.
This realization has similarly fueled a body of research into
the various incentive structures available to piecework employers
\cite{roy1953work}.

The parallels between the complaints of low pay among crowd workers and other on--demand workers
and the pieceworkers and later factory workers in the \nth{20} century
are inescapable.
We argue further that the \textit{causes} here
--- work decomposition,
work abstraction, and
flexibility ---
lead inexorably to low and declining pay for workers.

\subsubsection{Variable quality work}\label{sec:varQualWork}
Researchers have struggled with what we might generously call work of ``variable quality''
along two dimensions:
First, to use the characterization of one of these contributions,
``understanding malicious behavior''
\cite{MaliciousCrowdworkersGadiraju}.
While some work has cast workers as ``malicious'' agents,
the evidence thus far suggests that
workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
(a topic of discussion to which we'll return later)
\cite{uberAlgorithm}.
The second dimension of research in this space generally attempts
to eke out the highest quality work possible from workers
given the apparent difficulty in predicting work outcomes.

@@

Suffice it to say, then, that poor pay and poor work are linked,
and that we should not be surprised to find this relationship play out online as strongly as it does offline.
Indeed, \msb{finished sentence? \ali{Indeed.}}
